FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-01-25 epss_marmo.tex

\subsubsection{Planetary Surface proposed convention}
When willing to use FITS format for Planetary Surfaces the issue of rigorous
geographical representation must be addressed.
Planetary surface researchers for their mapping and analysis needs, commonly use
Geographical Information Systems (GIS).
In general, GIS applications excel in data interoperability even
though some have historically been anchored to Earth's spatial description.
FITS World Coordinate System representation\footnote{http://fits.gsfc.nasa.gov/fits\_wcs.html.}
simplifies the spatial coordinate description with respect to historical terrestrial
references.
There is no need for oblique projection definitions \citep{Snyder1987,calagreisenI}
as projection parameters (projection center or reference point)
describe the difference between the Mercator and
Transverse Mercator or Simple Cylindrical and
Equirectangular map projections.
There is no need for East or West positive longitude definitions as the pixel
conversion in world coordinates is set by a common
oriented matrix.

\begin{table}
\label{table:proj}
\caption{Projection names and codes already available in FITS suitable for planetary applications:
their translation in PDS vocabulary is also provided}
\centering
\begin{tabular}{l l l}
\hline
FITS Name$^{a}$ & FITS code$^{a}$ & PDS name$^{b}$ \\ 
\hline
Sanson-Flamsteed & SFL & Sinusoidal \\
Zenithal Equal-Area & ZEA & Lambert Azimuthal Equal Area \\
Conic ortomorphic & COO & Lambert Conformal Conic\\
Plate Carre & CAR & Equirectangular \\
Cylindrical Equal-Area & CEA & \\
Mercator & MER & Mercator, Oblique Mercator \\
Ortographic & SIN & Orthographic \\
Zenithal perspective & AZP & \\
Stereographic & STG & \\
\hline
\multicolumn{3}{l}{$^{a}$From \citet{calagreisenI}} \\
\multicolumn{3}{l}{$^{b}$From the PDS4 Data Dictionary\footnote{https://pds.jpl.nasa.gov/pds4/doc/dd/current/PDS4\_PDS\_DD\_1900.pdf}}
\end{tabular}
\end{table}

@@

\subsubsection{Best Practices and Examples}

>>>>

\section{Planetary Surface proposed convention}
When willing to use FITS format for Planetary Surfaces the issue of rigorous
geographical representation must be addressed.
Planetary surface researchers for their mapping and analysis needs, commonly use
Geographical Information Systems (GIS).
In general, GIS applications excel in data interoperability even
though some have historically been anchored to Earth's spatial description.
FITS World Coordinate System representation\footnote{http://fits.gsfc.nasa.gov/fits\_wcs.html.}
simplifies the spatial coordinate description with respect to historical terrestrial
references.
There is no need for oblique projection definitions \citep{Snyder1987,calagreisenI}
as projection parameters (projection center or reference point)
describe the difference between the Mercator and
Oblique Mercator or Simple Cylindrical and
Equirectangular map projections.
There is no need for East or West positive longitude definitions as the pixel
conversion in world coordinates is set by a common
oriented matrix.

\begin{table}
\label{table:wcskeys}
\caption{WCS FITS keywords in the Planetary Surface context}
\centering
\begin{tabular}{l l l l}
\hline
Keyword & Type & Definition & PDS4 \\
\hline
EQUINOX & real & & \\
RADESYS	& string & & \\
CRPIXn & real & & \\
CTYPEn & string & & \\
CRVALn & real & & \\
CDi\_j & real matrix & & \\
PCi\_j & real matrix & & \\
CDELTn & real & & \\
CUNITn & string & & \\
WCSNAME & string & & \\
CNAMEn & string (up to 68 characters) & & \\
\hline
\end{tabular}
\end{table}

\begin{table}
\label{table:proj}
\caption{Projection names and codes already available in FITS suitable for planetary applications:
their translation in PDS vocabulary is also provided}
\centering
\begin{tabular}{l l l}
\hline
FITS Name$^{a}$ & FITS code$^{a}$ & PDS name$^{b}$ \\ 
\hline
Sanson-Flamsteed & SFL & Sinusoidal \\
Zenithal Equal-Area & ZEA & Lambert Azimuthal Equal Area \\
Conic Ortomorphic & COO & Lambert Conformal Conic\\
Plate Carre & CAR & Equirectangular \\
Cylindrical Equal-Area & CEA & \textit{there is no CEA option in PDS4 neither in ISIS3}\\
Mercator & MER & Mercator, Oblique Mercator \\
Ortographic & SIN & Orthographic \\
Zenithal Perspective & AZP & General Vertical Near-sided Perspective \\
Stereographic & STG & Stereographic, Polar Stereographic \\
Gnomonic & TAN & Gnomonic \\
\hline
\multicolumn{3}{l}{$^{a}$From \citet{calagreisenI}} \\
\multicolumn{3}{l}{$^{b}$From the PDS4 Data Dictionary\footnote{https://pds.jpl.nasa.gov/pds4/doc/dd/current/PDS4\_PDS\_DD\_1900.pdf}}
\end{tabular}
\end{table}

@@

\subsection{Best Practices and Examples}
